%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Sortable Inc.} % Organization
    {Kitchener, Ontario} % Location
    {Jan. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote Javascript that was deployed to
            hundreds of millions of browsers (Sortable Ad Tags)}
        \item {Wrote Sortable's Accelerated Mobile Pages (AMP) integration}
        \item {Contributed to the \href{https://github.com/ampproject/amphtml}{AMP project}}
        \item {Built a new Ad Analytics view from the ground up using
            Apache Spark (processing of ad data),
            Presto DB and PostgreSQL (SQL database), Scala (backend) and Angular JS (frontend)}
        \item {Worked on data reporting in different timezone and
            increased granularity}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {Applyboard Inc.} % Organization
    {Kitchener, Ontario} % Location
    {May. 2016 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Full stack Ruby on Rails devlopment for Applyboard.com}
        \item {Implemented full-fledged features of site}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer} % Job title
    {Fluid Media Inc.}% Organization
    {Hamilton, Ontario} % Location
    {Sep. 2015 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Full stack Ruby on Rails development}
        \item {Learned how to integrate into tech company culture and work with teams on
projects using tools such as Git and Github.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
